Scan-Centric, Frequency-Based Method for Characterizing Peaks from Direct Injection FT-MS Experiments

### 2022-03-21 doc/peakcharacterization_manuscript.Rmd
just a few more tweaks to the figure, and I think we are good.

hpd_left_panel = wrap_plots(hpd_plots_2ecf$plots, ncol = 1)
hpd_right_panel = hpd_plots_2ecf$n %>%
  ggplot(aes(x = xcalibur,
             y = count,
             color = method)) +
  geom_point(size = 3) +
  labs(x = "Xcalibur peak count",
       y = "peak count") +
  theme(legend.position = c(0.1, 0.8))
hpd_left_panel | hpd_right_panel
```

`r figure_count$label_text("hpd_compare_fsd")`.
Comparison of HPD and high FSD sites in the ECF 2 sample.
Left: Peak plots for various peak processing modalities in a single HPD site. 
*xcalibur*: peaks exported from Thermo Xcalibur after averaging scans.
*scalevel_00*: Scan-level peak characterization without any density based filtering (see noperc_nonorm in Methods).
*scanlevel_99*: Scan-level peak characterization using the default point density filtering (see filtersd in Methods).
*scanlevel_99_lowsd*: Same as *scanlevel_99*, but removing any peaks marked as having a high frequency standard deviation.
*msnbase*: peak centroids generated from *MSnbase*.
Right: Scatterplot of peak counts across all of the HPDs detected in the ECF 2 sample against the Xcalibur peak counts.

@@

```{r increment_rsd}
figure_count$increment("rsd_method")
```

>>>>

hpd_left_panel = wrap_plots(hpd_plots_2ecf$plots, ncol = 1)
hpd_right_panel = hpd_plots_2ecf$n %>%
  ggplot(aes(x = xcalibur,
             y = count,
             color = method)) +
  geom_point(size = 3) +
  labs(x = "Xcalibur peak count",
       y = "peak count") +
  theme(legend.position = c(0.1, 0.8))
(hpd_left_panel | hpd_right_panel) + plot_annotation(tag_levels = "A")
```

`r figure_count$label_text("hpd_compare_fsd")`.
Comparison of HPD and high FSD sites in the ECF 2 sample.
**A** - **E**:Peak plots for various peak processing modalities in a single HPD site. 
**A**:*xcalibur* peaks exported from Thermo Xcalibur after averaging scans.
**B**:*scalevel_00*: Scan-level peak characterization without any density based filtering (see noperc_nonorm in Methods).
**C**:*scanlevel_99*: Scan-level peak characterization using the default point density filtering (see filtersd in Methods).
**D**:*scanlevel_99_lowsd*: Same as *scanlevel_99*, but removing any peaks marked as having a high frequency standard deviation.
**E**:*msnbase*: peak centroids generated from *MSnbase*.
**F**: Scatterplot of peak counts across all of the HPDs detected in the ECF 2 sample against the Xcalibur peak counts.

@@

```{r increment_rsd}
figure_count$increment("rsd_method")
table_count$increment("rsd_method")
```
